## Assessment 2
## Title
The purpose of this project is to analysis which weather event is need to prioritize resources across the United States.
Using the U.S. National Oceanic and Atmospheric Administration's (NOAA) storm database to analysis this project.
According to this data analysis, TORNADO is most harmful with respect to population health and also the greatest economic consequences.

## Synopsis
This analysis uses the fatalities and injuries as the measurement of the harm to the population health
and uses property damage(PROPDMG) and crop damage(CROPDMG) as the measurement of economic consequences

## Data Processing

# Read the raw data
```{r,echo=TRUE}
Data <- read.csv("./repdata-data-StormData.csv", header = TRUE)
```
# Make non-numeric FATALITIES/INJURIES into NA
```{r,echo=TRUE}
CleanData <- Data
CleanData$FATALITIES <- as.numeric(as.character(CleanData$FATALITIES))
CleanData$INJURIES <- as.numeric(as.character(CleanData$INJURIES))
```
# Group by the EVTYPE order by the sum of 
```{r,echo=TRUE}
CleanData$HARM <- apply(CleanData[,c("FATALITIES","INJURIES")],1,sum)
HARMGroup <- aggregate(data=CleanData, HARM~EVTYPE,FUN=sum,na.rm=TRUE)
HARMGroup <- HARMGroup[with(HARMGroup,order(-HARM)),]
HARMTop1 <-head(HARMGroup,1)
```

#  Make non-numeric PROPDMG/CROPDMG into NA
```{r,echo=TRUE}
CleanData$PROPDMG <- as.numeric(as.character(CleanData$PROPDMG))
CleanData$CROPDMG <- as.numeric(as.character(CleanData$CROPDMG))
```
# Creat a new variable for calculate the damage  
```{r,echo=TRUE}
PROPEXP <- data.frame(Index=c("","*","?","+","-","0","1","2","H","h","K","k","M","m","B","b"),PROPUnit=c(0,0,0,0,0,1,10,10^2,10^2,10^2,10^3,10^3,10^6,10^6,10^9,10^9))
CROPEXP <- data.frame(Index=c("","*","?","+","-","0","1,","2","H","h","K","k","M","m","B","b"),CROPUnit=c(0,0,0,0,0,1,10,10^2,10^2,10^2,10^3,10^3,10^6,10^6,10^9,10^9))
MergeUnit <- merge(CleanData, PROPEXP, by.x = "PROPDMGEXP", by.y = "Index",all.x=TRUE)
MergeUnit <- merge(MergeUnit, CROPEXP, by.x = "CROPDMGEXP", by.y = "Index",all.x=TRUE)
MergeUnit$Value <- MergeUnit$PROPDMG*MergeUnit$PROPUnit + MergeUnit$CROPDMG*MergeUnit$CROPUnit
```

# Group by the EVTYPE order by the sum of damage
```{r,echo=TRUE}
MergeGroup <- aggregate(data=MergeUnit, Value~EVTYPE,FUN=sum,na.rm=TRUE)
MergeGroup <- MergeGroup[with(MergeGroup,order(-Value)),]
Top1 <-head(MergeGroup,1)
```

## Results
* Across the United States, `r HARMTop1$EVTYPE` are most harmful with respect to population health.
* Across the United States, `r Top1$EVTYPE` have the greatest economic consequences
